Test

### 2016-07-22 Berkeley_PD_Stop.Rmd
complete cleaning

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library(dplyr)
library(stringr)
library(lubridate)
library(ggplot2)
library(reshape)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library(dplyr)
library(stringr)
library(lubridate)
library(ggplot2)
